---
output:
  github_document:
    html_preview: true
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# tdpcaTEP
An `R` package containing all code to reproduce the TEP data results in the paper
"Online Detection of Sparse Changes in High-Dimensional Data Streams Using Tailored Projections".
In addition, the package contains the files with the results we obtained
in the directories /results and /thresholds.
It is also an aim that this package can be used by others who want to test TDPCA
for their monitoring tasks, both for bootstrapping thresholds and testing performance
in terms of expected detection delays (EDD).

## Overview
Functionality:

* A function to reproduce the entire TEP data study.
* A function for finding thresholds for TDPCA by non-parametric bootstrapping.
* Summary and plot functions.

## Installation

You can install tdpcaTEP from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Tveten/tdpcaTEP")
```

The associated Tennessee Eastman Process data are too large to upload here and into the package, so it has to be downloaded manually.
1. Go to https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/6C3JR1
2. Download the files TEP_FaultFree_Training.RData and TEP_FaultFree_Training.RData.
3. Place these files in your working directory.

To reproduce figures from our result files, download the folders /results and
/thresholds from https://github.com/Tveten/tdpcaTEP and put them in your 
working directory before running the plot functions.

## Exported and documented functions
For more information, see the documentation of the functions below inside R.

* TEP_summary
* load_TEP_data_globally
* pfa_edd_table
* rl_density
* run_TEP_dpca
* run_TEP_sim
* tdpca_arl
* threshold_finder

The documentation in tpcaMonitoring is helpful to understand the internal functions
used in the functions above, as they are more or less the same.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tdpcaTEP)
# To run the entire TEP study, use run_TEP_sim().
# It will take a day or two on a regular computer, but the output from it is also contained in
# this package so that one can still get plots of results and study the results in more detail.
# Before running this example code, downloaded
# the results/ and thresholds/ directories from https://github.com/Tveten/tdpcaTEP
# and put them in your working directory.
# The code in run_TEP_sim() specifies in a simple way the simulation
# setup and the necessary steps in the study.

lag <- 5
fault_nr <- 15

# rl_density(lag, fault_nr)
TEP_summary(lag, fault_nr, sort_by = 'edd')

pfa_edd_table()

```
